%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\name{SAI PRASAD CH} % Your name
\address{(+91)~$\cdot$~9650001845 \\ saiprasad.ch@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Institute of Technology, Warangal } \hfill {\em April 2009} \\ 
B.Tech in Computer Science \& Engineering \\
Overall GPA: 7.00

{\bf New Generation Junior College, Hyderabad } \hfill {\em April 2004} \\ 
Intermediate Education (12th) in Maths, Physics \& Chemistry \\
Overall Percentage: 87.60

{\bf Chaitanya High School, Andhra Pradesh } \hfill {\em April 2002} \\ 
High School (10th) \\
Overall Percentage: 91.00

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Gwynnie Bee, Inc}{September 2012 - Present}{Software Engineer}{New Delhi}
Gwynnie Bee is an e-commerce {\bf startup} providing subscription of Women’s clothing.
\item {\bf Role}: Involved in design, develop, document and test of functionalities in customer-facing and
admin websites, and other internal tools.
\item {\bf Technologies used}: Node.js, Yahoo! Mojito, MySQL, Javascript, YUI 3, jQuery, Java, YUITest (Unit Testing), Selenium, Maven.
\item Working on streamlining the development in front-end and Node.js like establishing processes, setting up tools (JSHint, Unit Testing etc.) and generic modules (like Analytics, Profiler, Promise pattern etc), Node.js server monitoring.
\item End-to-end development of an API service for user feedbacks using Java and MySQL.
\item Worked on development of multiple features in the customer facing as well as admin site.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Adobe Systems, Inc}{April 2009 - September 2012}{Member of Technical Staff II}{Noida}
\item {\bf Adobe LeanPrint}
\item {\bf Role}: Complete responsibility and ownership of Updater and browser plugins of Adobe LeanPrint for Internet Explorer, Mozilla Firefox \& Google Chrome.
\item {\bf Technologies used}: C++, Javascript, jQuery, XUL.
\item Responsibilities in browser plguins include develop and improve content detection heuristics, performance tuning, usability improvement and security enhancements.
\item Complete implementation of Updater component, with primary focus on usability and security.
\item Automated build setup for regular builds (using Build Forge).
\item Handled multiple web based tools and internal tools that are needed for the team.
\item Worked closely with QE team, providing continuous support in the testing of product
including test case reviews, bug isolation.
\item Received a couple of {\bf Spot Awards} for recognition of my work on this product.
\item Helped with the development work of installer for the product.

\item {\bf Adobe PDF Driver}
\item Adobe PDF Driver is a print driver SDK that facilitates high quality printing of documents to PDF based RIPs on Windows and Mac.
\item {\bf Role}: Integral part of the core development team of the product on multiple platforms. Responsibilities include conceptualization, implementation of features, feature stabilization, memory leaks detection \& fixing, memory usage optimization and performance improvement, product documentation.
\item {\bf Technologies used}: C++, Objective C++, Windows Driver Kit, Actionscript 3, Flex 3, Flex 4, AIR.
\item {\bf Platforms}: Windows, Mac OS
\item {\bf Standards Involved}: XML Paper Specification (XPS), Portable Document Format (PDF), Job Description Format (JDF)
\item Worked as the only developer on the product for 15 months.
\item Received a {\bf Spot Award} for recognition of my work in the product.
\item Worked in fixing memory leaks, memory optimizations, and performance improvements.
\item Worked directly with customers on resolving their issues \& queries.
\item Involved in test case reviews and worked closely with the QA team, providing continuous
support to the testing of the product.
\item Automation of the build and testing processes.
\item Involved in writing documentation of the product.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{IBM - India Software Lab}{May 2008 - July 2008}{Academic Intern}{Bangalore}
\item Worked on developing the web-based user interface for IBM Master Data Management Server's Dashboard.
\item {\bf Technologies used}: HTML, JavaScript, Dojo Toolkit, dojox.gfx
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Application Development & C++, Win32 APIs, ActionScript  \\
Frontend Engineering & Javascript, jQuery, YUI, JSHint \\
Backend Engineering & Node.js, Yahoo! Mojito, PHP, CodeIgniter, Kohana \\
Databases & MySQL \\
Browser Extensions & Browser extensions and user scripts for Chrome \& Firefox  \\
Basic & Go, Java, Python, Android \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
